### 2014-01-14 talk/ecoop2009/abstract.tex
I'm no longer late today (at least not by more than 5 minutes)

\begin{abstract}
Implementing dynamically typed languages in an efficient way is a hard task.
Recent developments show that JIT compilers 
can exploit runtime type information to generate quite efficient code.
Unfortunately, writing a JIT compiler is far from being simple.

>>>>

\begin{abstract}
Writing an optimizing static compiler for dynamic languages is not an
easy task, since quite complex static analysis is required.
On the other hand, recent developments show that JIT compilers 
can exploit runtime type information to generate quite efficient code.
Unfortunately, writing a JIT compiler is far from being simple.

### 2014-01-14 talk/icooolps2009-dotnet/benchmarks.tex
I'm no longer late today (at least not by more than 5 minutes)

Moreover, for each benchmark we also show the time taken by running the
equivalent program written in C\#.\footnote{The sources for both TLC and C\#
  programs are available at:
  \texttt{http://codespeak.net/~antocuni/tlc-benchmarks/}}

@@

The difference in speed it is probably due to both the fact that the current
CLI backend emits slightly non-optimal code and that the underyling .NET JIT
compiler is highly optimized to handle bytecode generated by C\# compilers.

>>>>

The columns \emph{Interp/JIT2} and \emph{JIT2/C\#} measure the speedup of the
generated code compared to plain interpretation and of the equivalent C\#
program compared to the generated code, respectively.

Moreover, for each benchmark we also show the time taken by running the
equivalent program written in C\#.\footnote{The sources for both TLC and C\#
  programs are available at:
  \texttt{http://codespeak.net/$\sim$antocuni/tlc-benchmarks/}}

@@

The difference in speed is probably due to both the fact that the current
CLI backend emits slightly non-optimal code and that the underyling .NET JIT
compiler is highly optimized to handle bytecode generated by C\# compilers.
